### 2018-01-28 ApproxComp/sec-query.tex

We develop a data-driven approach, instead of filter-and-verification, to  identifying the most possible $k$ time intervals from $T \times (T + 1)/2$ time intervals, in which $T$ is the number of snapshots and k is a small constant, \eg 10. This is achieved by exploring the characteristics of time intervals involved with dense subgraphs based on the observation of {\em evolving convergence phenomenon} in traffic data, inspired by the convergent evolution in nature\footnote{\small \url{https://en.wikipedia.org/wiki/Convergent_evolution}}. That is, our method provides time intervals with probabilistic grantees, instead of exact ones like \kw{FAV}.   Using both real-life and synthetic data, we experimentally show that Our method \kw{FIDES} is over 1000 times faster than the state of the art solution  \kw{MEDEN}~\cite{BogdanovMS11}, while the quality of dense subgraphs found is comparable with  \kw{MEDEN} .

>>>>

We develop a data-driven approach, instead of filter-and-verification, to  identifying the most possible $k$ time intervals from $T \times (T + 1)/2$ time intervals, in which $T$ is the number of snapshots and k is a small constant, \eg 10. This is achieved by exploring the characteristics of time intervals involved with dense subgraphs based on the observation of {\em evolving convergence phenomenon} in traffic data, inspired by the convergent evolution in nature\footnote{\small \url{https://en.wikipedia.org/wiki/Convergent_evolution}}. That is, our method provides time intervals with probabilistic guarantees, instead of exact ones as \kw{FAV}.   Using both real-life and synthetic data, we experimentally show that our method \kw{FIDES} is over 1000 times faster than \kw{MEDEN}~\cite{BogdanovMS11}, while the quality of dense subgraphs found is comparable with  \kw{MEDEN} .
